---
title: "examenR"
author: "Carla Iranzo"
date: '2023-12-20'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

2. [4 points] Use the fibonacci function to compute the first 31 Fibonacci numbers (n from 0 to 30). Todo so, use a sequential approach and an approach taking advantage of the parallelization tools in R and compare the computing times. Which approach is preferrable? Write everything in a Rmd / qmd document and compile it to html.


Sequential approach

```{r}

set.seed(1234)
source("fibonacci.R")
sequential_times <- system.time({
  fib_seq <- sapply(0:30, fibonacci)
})

print(fib_seq)
print(sequential_times)

```

Parallel Approach

```{r message=FALSE, warning=FALSE}
library(doParallel)
library(doRNG)
source("fibonacci.R")

set.seed(1234)
cl <- makeCluster(detectCores())
parallel_times <- system.time({
  fib_par <- sapply(0:30, fibonacci)
})
stopCluster(cl)

print(fib_par)
print(parallel_times)
```

```{r}
comparison_table <- data.frame(
  Approach = c("Sequential", "Parallel"),
  Time = c(sequential_times[3], parallel_times[3])
)

print(comparison_table)

```

The computing time may vary in each execution but mostly, both computing times are nearly the same.

Github repository: https://github.com/carlairanzo/examenR